### 2022-05-26 chapters/programming_languages/web_frameworks.tex
add : tommti benchmark just a single draft have to readit later

\begin{longtable}{lll}
    \toprule
    framework        & language    & alternative implementations                        \\
    \midrule
    \endhead
    \midrule
    \multicolumn{3}{r}{{Continued on next page}}                                        \\
    \midrule
    \endfoot

    \bottomrule
    \endlastfoot
    pico.v           & V           &                                                    \\
    dylan            & Dylan       &                                                    \\
    sinatra-sequel   & Ruby        & postgres passenger-mri postgres-passenger-mri...   \\
    agoo             & Ruby        &                                                    \\
    rack             & Ruby        & unicorn falcon                                     \\
    h2o\_mruby       & Ruby        &                                                    \\
    rails            & Ruby        & postgresql unicorn                                 \\
    grape            & Ruby        & unicorn                                            \\
    roda-sequel      & Ruby        & postgres passenger-mri postgres-passenger-mri...   \\
    rack-sequel      & Ruby        & postgres passenger-mri postgres-passenger-mri...   \\
    sinatra          & Ruby        & postgres passenger-mri postgres-passenger-mri...   \\
    padrino          & Ruby        & unicorn                                            \\
    ninglex          & Common Lisp &                                                    \\
    ningle           & Common Lisp &                                                    \\
    woo              & Common Lisp &                                                    \\
    grails           & Groovy      &                                                    \\
    hot              & Groovy      & mongodb postgres mysql                             \\
    plack            & Perl        & async                                              \\
    kelp             & Perl        & mongodb                                            \\
    dancer           & Perl        &                                                    \\
    mojolicious      & Perl        &                                                    \\
    web-simple       & Perl        &                                                    \\
    cowboy           & Erlang      &                                                    \\
    elli             & Erlang      &                                                    \\
    chicagoboss      & Erlang      &                                                    \\
    mochiweb         & Erlang      &                                                    \\
    opium            & OCaml       & haproxy                                            \\
    morph            & OCaml       & static                                             \\
    webmachine       & OCaml       & haproxy                                            \\
    vertx-web-scala  & Scala       &                                                    \\
    http4s           & Scala       &                                                    \\
    akka-http        & Scala       & slick-postgres                                     \\
    fintrospect      & Scala       &                                                    \\
    finagle          & Scala       &                                                    \\
    colossus         & Scala       &                                                    \\
    finatra          & Scala       &                                                    \\
    blaze            & Scala       &                                                    \\
    play2-scala      & Scala       & netty anorm anorm-netty reactivemongo reactiv...   \\
    finch            & Scala       &                                                    \\
    scalene          & Scala       &                                                    \\
    cask             & Scala       &                                                    \\
    youi             & Scala       &                                                    \\
    httpbeast        & Nim         &                                                    \\
    prologue         & Nim         &                                                    \\
    basolato         & Nim         &                                                    \\
    jester           & Nim         &                                                    \\
    falco            & F\#         &                                                    \\
    frank            & F\#         &                                                    \\
    suave            & F\#         &                                                    \\
    giraffe          & F\#         & utf8json utf8direct stripped                       \\
    zebra            & F\#         & simple                                             \\
    vapor            & Swift       & fluent sql-kit postgres                            \\
    swift-nio        & Swift       &                                                    \\
    perfect          & Swift       & mysql postgresql mongodb                           \\
    kitura           & Swift       & postgres postgres-orm postgres-orm-codable mo...   \\
    racket           & Racket      &                                                    \\
    vsgi             & Vala        &                                                    \\
    valum            & Vala        &                                                    \\
    wsgi             & Python      &                                                    \\
    hug              & Python      &                                                    \\
    crax             & Python      &                                                    \\
    falcon           & Python      & py3 pypy2                                          \\
    uvicorn          & Python      &                                                    \\
    flask            & Python      & raw pypy pypy2 pypy2-raw nginx-uwsgi               \\
    responder        & Python      &                                                    \\
    klein            & Python      &                                                    \\
    blacksheep       & Python      &                                                    \\
    apidaora         & Python      & core                                               \\
    bottle           & Python      & pypy2 raw nginx-uwsgi                              \\
    japronto         & Python      &                                                    \\
    api\_hour        & Python      & mysql json dbs plaintext                           \\
    weppy            & Python      & py3 pypy2 nginx-uwsgi                              \\
    starlette        & Python      &                                                    \\
    emmett           & Python      &                                                    \\
    sanic            & Python      &                                                    \\
    aiohttp          & Python      & pg-raw                                             \\
    tornado          & Python      & pypy2 postgresql-raw py3 py3-uvloop                \\
    uwsgi            & Python      & nginx-uwsgi                                        \\
    pyramid          & Python      & py2                                                \\
    morepath         & Python      &                                                    \\
    vibora           & Python      &                                                    \\
    web2py           & Python      & optimized                                          \\
    django           & Python      & postgresql                                         \\
    cherrypy         & Python      & py3                                                \\
    eve              & Python      &                                                    \\
    webware          & Python      &                                                    \\
    spyne            & Python      & raw nginx-uwsgi                                    \\
    fastapi          & Python      & orjson                                             \\
    quart            & Python      & uvicorn                                            \\
    turbogears       & Python      &                                                    \\
    m-web-server     & mumps       &                                                    \\
    urweb            & Ur          & mysql cache mysql-cache                            \\
    rouille          & Rust        &                                                    \\
    warp-rust        & Rust        &                                                    \\
    thruster         & Rust        &                                                    \\
    ntex             & Rust        & db raw                                             \\
    iron             & Rust        &                                                    \\
    actix            & Rust        & core raw diesel pg                                 \\
    roa              & Rust        & core tokio diesel pg sqlx                          \\
    saphir           & Rust        &                                                    \\
    may-minihttp     & Rust        &                                                    \\
    rocket           & Rust        &                                                    \\
    tokio-minihttp   & Rust        &                                                    \\
    nickel           & Rust        &                                                    \\
    hyper            & Rust        & db                                                 \\
    gotham           & Rust        &                                                    \\
    kooby            & Kotlin      &                                                    \\
    pronghorn        & Kotlin      &                                                    \\
    http4k           & Kotlin      & apache apache4 jetty ktorcio ktornetty netty ...   \\
    ktor             & Kotlin      & jetty cio jasync reactivepg                        \\
    hexagon          & Kotlin      & resin-mongodb jetty-postgresql resin-postgresql    \\
    elixir-plug-ecto & Elixir      &                                                    \\
    phoenix          & Elixir      &                                                    \\
    fiber            & Go          & prefork                                            \\
    webgo            & Go          &                                                    \\
    gnet             & Go          &                                                    \\
    goframe          & Go          &                                                    \\
    revel            & Go          & fast raw jet qbs                                   \\
    echo             & Go          &                                                    \\
    gramework        & Go          &                                                    \\
    gin              & Go          & scratch                                            \\
    atreugo          & Go          & prefork                                            \\
    beego            & Go          & orm-mysql                                          \\
    kami             & Go          &                                                    \\
    falcore          & Go          &                                                    \\
    goji             & Go          &                                                    \\
    clevergo         & Go          &                                                    \\
    fasthttp         & Go          & prefork                                            \\
    aah              & Go          & mysql postgresql                                   \\
    gearbox          & Go          & prefork                                            \\
    martini          & Go          &                                                    \\
    go               & Go          & pgx pgx-easyjson pgx-quicktemplate pgx-prefor...   \\
    evio             & Go          & stdlib                                             \\
    chi              & Go          & scratch prefork gojay gojay-prefork sjson sjs...   \\
    warp             & Haskell     & hasql mysql-haskell                                \\
    yesod            & Haskell     & mongodb-raw                                        \\
    wizzardo-inline  & Haskell     &                                                    \\
    snap             & Haskell     &                                                    \\
    spock            & Haskell     &                                                    \\
    ihp              & Haskell     &                                                    \\
    servant          & Haskell     & beam psql-simple                                   \\
    stream           & Dart        &                                                    \\
    start            & Dart        &                                                    \\
    angel            & Dart        & postgres                                           \\
    redstone         & Dart        & mongodb                                            \\
    dart             & Dart        &                                                    \\
    aqueduct         & Dart        &                                                    \\
    aspcore-vb-mw    & VB          & ado-pg ado-my                                      \\
    spider-gazelle   & Crystal     &                                                    \\
    toro             & Crystal     &                                                    \\
    onyx             & Crystal     &                                                    \\
    h2o.cr           & Crystal     &                                                    \\
    kemal            & Crystal     & concurrent-queries                                 \\
    lucky            & Crystal     &                                                    \\
    crystal          & Crystal     & radix                                              \\
    grip             & Crystal     &                                                    \\
    orion            & Crystal     &                                                    \\
    amber            & Crystal     &                                                    \\
    raze             & Crystal     &                                                    \\
    collie           & D           & ldc                                                \\
    vibed            & D           & dmd-pgsql ldc ldc-pgsql                            \\
    hunt             & D           &                                                    \\
    macchiato        & Clojure     &                                                    \\
    aleph            & Clojure     &                                                    \\
    luminus          & Clojure     &                                                    \\
    pedestal         & Clojure     &                                                    \\
    compojure        & Clojure     & raw                                                \\
    http-kit         & Clojure     & raw                                                \\
    duct             & Clojure     & mongodb httpkit aleph immutant                     \\
    reitit           & Clojure     & jdbc async                                         \\
    nestjs           & TypeScript  & mysql mongo fastify fastify-mysql fastify-mongo    \\
    typescript-rest  & TypeScript  &                                                    \\
    deno             & TypeScript  &                                                    \\
    dropwizard       & Java        & mongodb postgres jdbi-postgres                     \\
    httpserver       & Java        & postgres                                           \\
    quarkus          & Java        & pgclient                                           \\
    jooby            & Java        & netty jaxrs jetty pgclient                         \\
    undertow         & Java        & postgresql                                         \\
    tapestry         & Java        &                                                    \\
    vertx-web        & Java        & mongodb postgres susom-postgres                    \\
    jlhttp           & Java        & postgres                                           \\
    voovan           & Java        &                                                    \\
    play2-java       & Java        & netty ebean-hikaricp ebean-hikaricp-netty jpa...   \\
    officefloor      & Java        & raw tpr micro thread\_affinity netty spring\_data  \\
    jersey           & Java        &                                                    \\
    proteus          & Java        & mysql                                              \\
    light-4j         & Java        &                                                    \\
    activeweb        & Java        & jackson                                            \\
    minijax          & Java        &                                                    \\
    jetty            & Java        & servlet                                            \\
    spark            & Java        &                                                    \\
    grizzly          & Java        & jersey                                             \\
    servlet          & Java        & lib-native mysql postgresql                        \\
    tio-mvc          & Java        &                                                    \\
    baratine         & Java        &                                                    \\
    servicetalk      & Java        &                                                    \\
    play1            & Java        &                                                    \\
    ninja-standalone & Java        &                                                    \\
    nanohttpd        & Java        &                                                    \\
    simple-server    & Java        &                                                    \\
    restexpress      & Java        & mysql-raw                                          \\
    javalin          & Java        &                                                    \\
    jawn             & Java        &                                                    \\
    redkale          & Java        & postgres                                           \\
    revenj-jvm       & Java        &                                                    \\
    spring-webflux   & Java        & mongo pgclient rxjdbc jdbc                         \\
    firenio          & Java        & http-lite                                          \\
    curacao          & Java        &                                                    \\
    bayou            & Java        &                                                    \\
    wizzardo-http    & Java        &                                                    \\
    netty            & Java        &                                                    \\
    armeria          & Java        &                                                    \\
    vertx            & Java        & postgres                                           \\
    comsat           & Java        & servlet-undertow webactors-netty webactors-un...   \\
    ratpack          & Java        & jdbc pgclient                                      \\
    wicket           & Java        &                                                    \\
    wildfly-ee       & Java        &                                                    \\
    undertow-jersey  & Java        & hikaricp                                           \\
    micronaut        & Java        &                                                    \\
    servlet3         & Java        & sync                                               \\
    act              & Java        & hibernate-pgsql hibernate-pgsql-rythm hiberna...   \\
    blade            & Java        &                                                    \\
    rapidoid         & Java        & mysql postgres http-fast                           \\
    smart-socket     & Java        &                                                    \\
    gemini           & Java        & mysql postgres                                     \\
    greenlightning   & Java        &                                                    \\
    helidon          & Java        &                                                    \\
    spring           & Java        & jpa mongo                                          \\
    codeigniter      & PHP         &                                                    \\
    fat-free         & PHP         & raw                                                \\
    php              & PHP         & activerecord raw7-tcp pgsql-raw h2o unit pool...   \\
    cakephp          & PHP         &                                                    \\
    ubiquity         & PHP         & workerman swoole swoole-mysql roadrunner road...   \\
    fuel             & PHP         &                                                    \\
    sw-fw-less       & PHP         &                                                    \\
    hyperf           & PHP         & raw micro                                          \\
    kumbiaphp        & PHP         & raw workerman workerman-mysql                      \\
    workerman        & PHP         & pgsql async                                        \\
    lumen            & PHP         & swoole                                             \\
    peachpie         & PHP         &                                                    \\
    yii2             & PHP         & raw                                                \\
    php-ngx          & PHP         & mysql pgsql async                                  \\
    laravel          & PHP         & swoole                                             \\
    symfony          & PHP         & raw swoole                                         \\
    imi              & PHP         & query-builder raw                                  \\
    webman           & PHP         &                                                    \\
    phalcon          & PHP         & mongodb micro                                      \\
    slim             & PHP         &                                                    \\
    amp              & PHP         &                                                    \\
    hhvm             & PHP         &                                                    \\
    spiral           & PHP         &                                                    \\
    swoole           & PHP         & postgres no-async                                  \\
    hamlet           & PHP         & swoole workerman                                   \\
    simps            & PHP         & micro                                              \\
    one              & PHP         &                                                    \\
    zend             & PHP         &                                                    \\
    phpixie          & PHP         &                                                    \\
    comet            & PHP         & mysql                                              \\
    nginx            & C           &                                                    \\
    onion            & C           &                                                    \\
    duda             & C           &                                                    \\
    libreactor       & C           & server                                             \\
    lwan             & C           & lua                                                \\
    h2o              & C           &                                                    \\
    facil\_io        & C           &                                                    \\
    octane           & C           &                                                    \\
    polkadot         & JavaScript  & mysql postgres mongodb                             \\
    restify          & JavaScript  &                                                    \\
    hapi             & JavaScript  & nginx mysql postgres                               \\
    nodejs           & JavaScript  & chakra mongodb mongodb-raw mysql postgres          \\
    restana          & JavaScript  &                                                    \\
    es4x             & JavaScript  &                                                    \\
    sailsjs          & JavaScript  & postgres                                           \\
    just             & JavaScript  &                                                    \\
    fastify          & JavaScript  & mysql postgres                                     \\
    ringojs          & JavaScript  & convenient                                         \\
    express          & JavaScript  & chakra mongodb mysql postgres graphql-mysql g...   \\
    koa              & JavaScript  & mysql postgres                                     \\
    0http            & JavaScript  &                                                    \\
    openresty        & Lua         &                                                    \\
    octopus          & Lua         &                                                    \\
    lapis            & Lua         &                                                    \\
    easyrpc          & C\#         &                                                    \\
    aspcore-mono     & C\#         & pg mw mw-pg mw-my mvc mvc-pg mvc-my                \\
    servicestack     & C\#         &                                                    \\
    tetsuweb         & C\#         &                                                    \\
    beetlex          & C\#         & core core-updb debug                               \\
    aspcore          & C\#         & pgo ado-pg ado-pg-up pgo-pg pgo-pg-up mw mw-j...   \\
    revenj           & C\#         &                                                    \\
    carter           & C\#         &                                                    \\
    aspnet-mono-ngx  & C\#         & jn ss my my-ef                                     \\
    genhttp          & C\#         &                                                    \\
    ben              & C\#         & pg                                                 \\
    evhttp-sharp     & C\#         &                                                    \\
    zysocket-v       & C\#         &                                                    \\
    nancy            & C\#         & netcore                                            \\
    aspcore-corert   & C\#         &                                                    \\
    cuehttp          & C++         &                                                    \\
    libhttpserver    & C++         &                                                    \\
    ffead-cpp        & C++         & mongo-raw lithium cinatra drogon libreactor h...   \\
    lithium          & C++         & postgres postgres-batch                            \\
    wt               & C++         & postgres                                           \\
    treefrog         & C++         & postgres mongodb                                   \\
    ulib             & C++         & plaintext\_fit json json\_fit mysql postgres po... \\
    cppcms           & C++         & postgres                                           \\
    oatpp            & C++         & no-mp async async-no-mp                            \\
    poco             & C++         &                                                    \\
    silicon          & C++         &                                                    \\
    cutelyst         & C++         & pf-apg pf-pg pf-my thread thread-apg thread-p...   \\
    drogon           & C++         & core                                               \\
    cinatra          & C++         &                                                    \\
    libsniper        & C++         &                                                    \\
    cpoll\_cppsp     & C++         & raw postgres-raw postgres-raw-threadpool           \\
\end{longtable}

>>>>

% \begin{longtable}{lll}
%     \toprule
%     framework        & language    & alternative implementations                        \\
%     \midrule
%     \endhead
%     \midrule
%     \multicolumn{3}{r}{{Continued on next page}}                                        \\
%     \midrule
%     \endfoot

%     \bottomrule
%     \endlastfoot
%     pico.v           & V           &                                                    \\
%     dylan            & Dylan       &                                                    \\
%     sinatra-sequel   & Ruby        & postgres passenger-mri postgres-passenger-mri...   \\
%     agoo             & Ruby        &                                                    \\
%     rack             & Ruby        & unicorn falcon                                     \\
%     h2o\_mruby       & Ruby        &                                                    \\
%     rails            & Ruby        & postgresql unicorn                                 \\
%     grape            & Ruby        & unicorn                                            \\
%     roda-sequel      & Ruby        & postgres passenger-mri postgres-passenger-mri...   \\
%     rack-sequel      & Ruby        & postgres passenger-mri postgres-passenger-mri...   \\
%     sinatra          & Ruby        & postgres passenger-mri postgres-passenger-mri...   \\
%     padrino          & Ruby        & unicorn                                            \\
%     ninglex          & Common Lisp &                                                    \\
%     ningle           & Common Lisp &                                                    \\
%     woo              & Common Lisp &                                                    \\
%     grails           & Groovy      &                                                    \\
%     hot              & Groovy      & mongodb postgres mysql                             \\
%     plack            & Perl        & async                                              \\
%     kelp             & Perl        & mongodb                                            \\
%     dancer           & Perl        &                                                    \\
%     mojolicious      & Perl        &                                                    \\
%     web-simple       & Perl        &                                                    \\
%     cowboy           & Erlang      &                                                    \\
%     elli             & Erlang      &                                                    \\
%     chicagoboss      & Erlang      &                                                    \\
%     mochiweb         & Erlang      &                                                    \\
%     opium            & OCaml       & haproxy                                            \\
%     morph            & OCaml       & static                                             \\
%     webmachine       & OCaml       & haproxy                                            \\
%     vertx-web-scala  & Scala       &                                                    \\
%     http4s           & Scala       &                                                    \\
%     akka-http        & Scala       & slick-postgres                                     \\
%     fintrospect      & Scala       &                                                    \\
%     finagle          & Scala       &                                                    \\
%     colossus         & Scala       &                                                    \\
%     finatra          & Scala       &                                                    \\
%     blaze            & Scala       &                                                    \\
%     play2-scala      & Scala       & netty anorm anorm-netty reactivemongo reactiv...   \\
%     finch            & Scala       &                                                    \\
%     scalene          & Scala       &                                                    \\
%     cask             & Scala       &                                                    \\
%     youi             & Scala       &                                                    \\
%     httpbeast        & Nim         &                                                    \\
%     prologue         & Nim         &                                                    \\
%     basolato         & Nim         &                                                    \\
%     jester           & Nim         &                                                    \\
%     falco            & F\#         &                                                    \\
%     frank            & F\#         &                                                    \\
%     suave            & F\#         &                                                    \\
%     giraffe          & F\#         & utf8json utf8direct stripped                       \\
%     zebra            & F\#         & simple                                             \\
%     vapor            & Swift       & fluent sql-kit postgres                            \\
%     swift-nio        & Swift       &                                                    \\
%     perfect          & Swift       & mysql postgresql mongodb                           \\
%     kitura           & Swift       & postgres postgres-orm postgres-orm-codable mo...   \\
%     racket           & Racket      &                                                    \\
%     vsgi             & Vala        &                                                    \\
%     valum            & Vala        &                                                    \\
%     wsgi             & Python      &                                                    \\
%     hug              & Python      &                                                    \\
%     crax             & Python      &                                                    \\
%     falcon           & Python      & py3 pypy2                                          \\
%     uvicorn          & Python      &                                                    \\
%     flask            & Python      & raw pypy pypy2 pypy2-raw nginx-uwsgi               \\
%     responder        & Python      &                                                    \\
%     klein            & Python      &                                                    \\
%     blacksheep       & Python      &                                                    \\
%     apidaora         & Python      & core                                               \\
%     bottle           & Python      & pypy2 raw nginx-uwsgi                              \\
%     japronto         & Python      &                                                    \\
%     api\_hour        & Python      & mysql json dbs plaintext                           \\
%     weppy            & Python      & py3 pypy2 nginx-uwsgi                              \\
%     starlette        & Python      &                                                    \\
%     emmett           & Python      &                                                    \\
%     sanic            & Python      &                                                    \\
%     aiohttp          & Python      & pg-raw                                             \\
%     tornado          & Python      & pypy2 postgresql-raw py3 py3-uvloop                \\
%     uwsgi            & Python      & nginx-uwsgi                                        \\
%     pyramid          & Python      & py2                                                \\
%     morepath         & Python      &                                                    \\
%     vibora           & Python      &                                                    \\
%     web2py           & Python      & optimized                                          \\
%     django           & Python      & postgresql                                         \\
%     cherrypy         & Python      & py3                                                \\
%     eve              & Python      &                                                    \\
%     webware          & Python      &                                                    \\
%     spyne            & Python      & raw nginx-uwsgi                                    \\
%     fastapi          & Python      & orjson                                             \\
%     quart            & Python      & uvicorn                                            \\
%     turbogears       & Python      &                                                    \\
%     m-web-server     & mumps       &                                                    \\
%     urweb            & Ur          & mysql cache mysql-cache                            \\
%     rouille          & Rust        &                                                    \\
%     warp-rust        & Rust        &                                                    \\
%     thruster         & Rust        &                                                    \\
%     ntex             & Rust        & db raw                                             \\
%     iron             & Rust        &                                                    \\
%     actix            & Rust        & core raw diesel pg                                 \\
%     roa              & Rust        & core tokio diesel pg sqlx                          \\
%     saphir           & Rust        &                                                    \\
%     may-minihttp     & Rust        &                                                    \\
%     rocket           & Rust        &                                                    \\
%     tokio-minihttp   & Rust        &                                                    \\
%     nickel           & Rust        &                                                    \\
%     hyper            & Rust        & db                                                 \\
%     gotham           & Rust        &                                                    \\
%     kooby            & Kotlin      &                                                    \\
%     pronghorn        & Kotlin      &                                                    \\
%     http4k           & Kotlin      & apache apache4 jetty ktorcio ktornetty netty ...   \\
%     ktor             & Kotlin      & jetty cio jasync reactivepg                        \\
%     hexagon          & Kotlin      & resin-mongodb jetty-postgresql resin-postgresql    \\
%     elixir-plug-ecto & Elixir      &                                                    \\
%     phoenix          & Elixir      &                                                    \\
%     fiber            & Go          & prefork                                            \\
%     webgo            & Go          &                                                    \\
%     gnet             & Go          &                                                    \\
%     goframe          & Go          &                                                    \\
%     revel            & Go          & fast raw jet qbs                                   \\
%     echo             & Go          &                                                    \\
%     gramework        & Go          &                                                    \\
%     gin              & Go          & scratch                                            \\
%     atreugo          & Go          & prefork                                            \\
%     beego            & Go          & orm-mysql                                          \\
%     kami             & Go          &                                                    \\
%     falcore          & Go          &                                                    \\
%     goji             & Go          &                                                    \\
%     clevergo         & Go          &                                                    \\
%     fasthttp         & Go          & prefork                                            \\
%     aah              & Go          & mysql postgresql                                   \\
%     gearbox          & Go          & prefork                                            \\
%     martini          & Go          &                                                    \\
%     go               & Go          & pgx pgx-easyjson pgx-quicktemplate pgx-prefor...   \\
%     evio             & Go          & stdlib                                             \\
%     chi              & Go          & scratch prefork gojay gojay-prefork sjson sjs...   \\
%     warp             & Haskell     & hasql mysql-haskell                                \\
%     yesod            & Haskell     & mongodb-raw                                        \\
%     wizzardo-inline  & Haskell     &                                                    \\
%     snap             & Haskell     &                                                    \\
%     spock            & Haskell     &                                                    \\
%     ihp              & Haskell     &                                                    \\
%     servant          & Haskell     & beam psql-simple                                   \\
%     stream           & Dart        &                                                    \\
%     start            & Dart        &                                                    \\
%     angel            & Dart        & postgres                                           \\
%     redstone         & Dart        & mongodb                                            \\
%     dart             & Dart        &                                                    \\
%     aqueduct         & Dart        &                                                    \\
%     aspcore-vb-mw    & VB          & ado-pg ado-my                                      \\
%     spider-gazelle   & Crystal     &                                                    \\
%     toro             & Crystal     &                                                    \\
%     onyx             & Crystal     &                                                    \\
%     h2o.cr           & Crystal     &                                                    \\
%     kemal            & Crystal     & concurrent-queries                                 \\
%     lucky            & Crystal     &                                                    \\
%     crystal          & Crystal     & radix                                              \\
%     grip             & Crystal     &                                                    \\
%     orion            & Crystal     &                                                    \\
%     amber            & Crystal     &                                                    \\
%     raze             & Crystal     &                                                    \\
%     collie           & D           & ldc                                                \\
%     vibed            & D           & dmd-pgsql ldc ldc-pgsql                            \\
%     hunt             & D           &                                                    \\
%     macchiato        & Clojure     &                                                    \\
%     aleph            & Clojure     &                                                    \\
%     luminus          & Clojure     &                                                    \\
%     pedestal         & Clojure     &                                                    \\
%     compojure        & Clojure     & raw                                                \\
%     http-kit         & Clojure     & raw                                                \\
%     duct             & Clojure     & mongodb httpkit aleph immutant                     \\
%     reitit           & Clojure     & jdbc async                                         \\
%     nestjs           & TypeScript  & mysql mongo fastify fastify-mysql fastify-mongo    \\
%     typescript-rest  & TypeScript  &                                                    \\
%     deno             & TypeScript  &                                                    \\
%     dropwizard       & Java        & mongodb postgres jdbi-postgres                     \\
%     httpserver       & Java        & postgres                                           \\
%     quarkus          & Java        & pgclient                                           \\
%     jooby            & Java        & netty jaxrs jetty pgclient                         \\
%     undertow         & Java        & postgresql                                         \\
%     tapestry         & Java        &                                                    \\
%     vertx-web        & Java        & mongodb postgres susom-postgres                    \\
%     jlhttp           & Java        & postgres                                           \\
%     voovan           & Java        &                                                    \\
%     play2-java       & Java        & netty ebean-hikaricp ebean-hikaricp-netty jpa...   \\
%     officefloor      & Java        & raw tpr micro thread\_affinity netty spring\_data  \\
%     jersey           & Java        &                                                    \\
%     proteus          & Java        & mysql                                              \\
%     light-4j         & Java        &                                                    \\
%     activeweb        & Java        & jackson                                            \\
%     minijax          & Java        &                                                    \\
%     jetty            & Java        & servlet                                            \\
%     spark            & Java        &                                                    \\
%     grizzly          & Java        & jersey                                             \\
%     servlet          & Java        & lib-native mysql postgresql                        \\
%     tio-mvc          & Java        &                                                    \\
%     baratine         & Java        &                                                    \\
%     servicetalk      & Java        &                                                    \\
%     play1            & Java        &                                                    \\
%     ninja-standalone & Java        &                                                    \\
%     nanohttpd        & Java        &                                                    \\
%     simple-server    & Java        &                                                    \\
%     restexpress      & Java        & mysql-raw                                          \\
%     javalin          & Java        &                                                    \\
%     jawn             & Java        &                                                    \\
%     redkale          & Java        & postgres                                           \\
%     revenj-jvm       & Java        &                                                    \\
%     spring-webflux   & Java        & mongo pgclient rxjdbc jdbc                         \\
%     firenio          & Java        & http-lite                                          \\
%     curacao          & Java        &                                                    \\
%     bayou            & Java        &                                                    \\
%     wizzardo-http    & Java        &                                                    \\
%     netty            & Java        &                                                    \\
%     armeria          & Java        &                                                    \\
%     vertx            & Java        & postgres                                           \\
%     comsat           & Java        & servlet-undertow webactors-netty webactors-un...   \\
%     ratpack          & Java        & jdbc pgclient                                      \\
%     wicket           & Java        &                                                    \\
%     wildfly-ee       & Java        &                                                    \\
%     undertow-jersey  & Java        & hikaricp                                           \\
%     micronaut        & Java        &                                                    \\
%     servlet3         & Java        & sync                                               \\
%     act              & Java        & hibernate-pgsql hibernate-pgsql-rythm hiberna...   \\
%     blade            & Java        &                                                    \\
%     rapidoid         & Java        & mysql postgres http-fast                           \\
%     smart-socket     & Java        &                                                    \\
%     gemini           & Java        & mysql postgres                                     \\
%     greenlightning   & Java        &                                                    \\
%     helidon          & Java        &                                                    \\
%     spring           & Java        & jpa mongo                                          \\
%     codeigniter      & PHP         &                                                    \\
%     fat-free         & PHP         & raw                                                \\
%     php              & PHP         & activerecord raw7-tcp pgsql-raw h2o unit pool...   \\
%     cakephp          & PHP         &                                                    \\
%     ubiquity         & PHP         & workerman swoole swoole-mysql roadrunner road...   \\
%     fuel             & PHP         &                                                    \\
%     sw-fw-less       & PHP         &                                                    \\
%     hyperf           & PHP         & raw micro                                          \\
%     kumbiaphp        & PHP         & raw workerman workerman-mysql                      \\
%     workerman        & PHP         & pgsql async                                        \\
%     lumen            & PHP         & swoole                                             \\
%     peachpie         & PHP         &                                                    \\
%     yii2             & PHP         & raw                                                \\
%     php-ngx          & PHP         & mysql pgsql async                                  \\
%     laravel          & PHP         & swoole                                             \\
%     symfony          & PHP         & raw swoole                                         \\
%     imi              & PHP         & query-builder raw                                  \\
%     webman           & PHP         &                                                    \\
%     phalcon          & PHP         & mongodb micro                                      \\
%     slim             & PHP         &                                                    \\
%     amp              & PHP         &                                                    \\
%     hhvm             & PHP         &                                                    \\
%     spiral           & PHP         &                                                    \\
%     swoole           & PHP         & postgres no-async                                  \\
%     hamlet           & PHP         & swoole workerman                                   \\
%     simps            & PHP         & micro                                              \\
%     one              & PHP         &                                                    \\
%     zend             & PHP         &                                                    \\
%     phpixie          & PHP         &                                                    \\
%     comet            & PHP         & mysql                                              \\
%     nginx            & C           &                                                    \\
%     onion            & C           &                                                    \\
%     duda             & C           &                                                    \\
%     libreactor       & C           & server                                             \\
%     lwan             & C           & lua                                                \\
%     h2o              & C           &                                                    \\
%     facil\_io        & C           &                                                    \\
%     octane           & C           &                                                    \\
%     polkadot         & JavaScript  & mysql postgres mongodb                             \\
%     restify          & JavaScript  &                                                    \\
%     hapi             & JavaScript  & nginx mysql postgres                               \\
%     nodejs           & JavaScript  & chakra mongodb mongodb-raw mysql postgres          \\
%     restana          & JavaScript  &                                                    \\
%     es4x             & JavaScript  &                                                    \\
%     sailsjs          & JavaScript  & postgres                                           \\
%     just             & JavaScript  &                                                    \\
%     fastify          & JavaScript  & mysql postgres                                     \\
%     ringojs          & JavaScript  & convenient                                         \\
%     express          & JavaScript  & chakra mongodb mysql postgres graphql-mysql g...   \\
%     koa              & JavaScript  & mysql postgres                                     \\
%     0http            & JavaScript  &                                                    \\
%     openresty        & Lua         &                                                    \\
%     octopus          & Lua         &                                                    \\
%     lapis            & Lua         &                                                    \\
%     easyrpc          & C\#         &                                                    \\
%     aspcore-mono     & C\#         & pg mw mw-pg mw-my mvc mvc-pg mvc-my                \\
%     servicestack     & C\#         &                                                    \\
%     tetsuweb         & C\#         &                                                    \\
%     beetlex          & C\#         & core core-updb debug                               \\
%     aspcore          & C\#         & pgo ado-pg ado-pg-up pgo-pg pgo-pg-up mw mw-j...   \\
%     revenj           & C\#         &                                                    \\
%     carter           & C\#         &                                                    \\
%     aspnet-mono-ngx  & C\#         & jn ss my my-ef                                     \\
%     genhttp          & C\#         &                                                    \\
%     ben              & C\#         & pg                                                 \\
%     evhttp-sharp     & C\#         &                                                    \\
%     zysocket-v       & C\#         &                                                    \\
%     nancy            & C\#         & netcore                                            \\
%     aspcore-corert   & C\#         &                                                    \\
%     cuehttp          & C++         &                                                    \\
%     libhttpserver    & C++         &                                                    \\
%     ffead-cpp        & C++         & mongo-raw lithium cinatra drogon libreactor h...   \\
%     lithium          & C++         & postgres postgres-batch                            \\
%     wt               & C++         & postgres                                           \\
%     treefrog         & C++         & postgres mongodb                                   \\
%     ulib             & C++         & plaintext\_fit json json\_fit mysql postgres po... \\
%     cppcms           & C++         & postgres                                           \\
%     oatpp            & C++         & no-mp async async-no-mp                            \\
%     poco             & C++         &                                                    \\
%     silicon          & C++         &                                                    \\
%     cutelyst         & C++         & pf-apg pf-pg pf-my thread thread-apg thread-p...   \\
%     drogon           & C++         & core                                               \\
%     cinatra          & C++         &                                                    \\
%     libsniper        & C++         &                                                    \\
%     cpoll\_cppsp     & C++         & raw postgres-raw postgres-raw-threadpool           \\
% \end{longtable}
